---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# STA 326 2.0/ ASP 454 2.0/ CSC 381 2.0 Programming and Data Analysis with R

## Mid Semester Examination Assignment  - 30 Marks


### Individual project: Coronavirus country report

The project represents 30% of your final grade for STA 326 2.0/ ASP 454 2.0/ CSC 381 2.0.

### 1. Guidelines

I have assigned a country to each of you. You need to write a brief report by analyzing coronavirus data for the country that I have assigned. The report should be written in Rmarkdown and the output format should be HTML. 

In order to view name of the country corresponds to your index number use the steps give below:

**Step 1**

Install `devtools` package.

```r
install.packages("devtools")
```

**Step 2**

Type the following code to get access to the `sta3262` package. This package provides a function to view the country. Please note that you may have  `sta3262` already installed in to your machine. However, you should reinstall `sta3262` in order to get access to the updated information.

```r
library(devtools)
devtools::install_github("thiyangt/sta3262")

```

**Step 3**

Load the `sta3262` using the command

```{r, comment=NA}
library(sta3262)
```


**Step 4**

To view your country, 

```{r, comment=NA, eval=FALSE}
get_individual_project_country("AS2021000") # type your index no. within ""
```

**Please send me an email if your index number is not in the list or if the function outputs** character(0) before July 29, 2024.

### 2. To obtain coronavirus data corresponds to your country

```r
install.packages("coronavirus")
library(coronavirus)
data("coronavirus")
```

You can download coronavirus data from the coronavirus package in R.  Filter necessary data.


### 3. Project content:

i. Brief introduction of the country:

ii. Exploratory Data Analysis

-	Visualization of death, confirmed, recovered, active cases
-	Comparison with other countries
-	etc

iii. Conclusions and Discussion

iv. References


Please do not include any external images.

### 4. Marks


- Content: 30 Marks (Data Analysis and interpretation 20, Overall format - 10)

- Reports that are AI-generated or plagiarized will receive zero marks.

### 5. Submission


Please submit .rmd file and .html file. Please name the files using your index number.

Example: AS2021000.rmd and AS2021000.html

- Upload both the HTML and RMarkdown files to the LMS and Google Classroom.


### 5. Deadline

2 August 2024, 8.00AM (IST)

It is the student’s responsibility to manage their time effectively to ensure that they have enough time to complete the assignment within the given timeframe. This includes allocating enough time to research, plan, and write the assignment, as well as allowing for unexpected circumstances or delays. It is important for students to plan their workload and prioritize their assignments to ensure that they are able to complete them on time and to the best of their ability.

**Late submission:** Submitting late work will be penalized by 1 mark per day. I will not accept any submissions after August 5, 2024.

**Extensions will be made in exceptional circumstances only.**

## Requesting a deadline extension

> You are allowed to apply for a deadline extension for the assignment under the following conditions only.

**Category A**

An illness that requires the student to miss all of his or her classes for 2 days or more.

**Category B**

A period of grief for the loss of a family member or friend.

**Category C**

A family emergency.

Valid documentation of proof is required **prior** to the assignment deadline.

The philosophy driving our late policy has three goals

-   Keep things fair.

-   Encourage good time management.

-   Encouragement and appreciation of on-time submission students.

Please submit your request along with the necessary evidence on or before August 1, 2024.

## Help Desk

If you have any questions, please feel free to seek clarification during the practical session on Monday, July 29, 2024.


