---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# STA 326 2.0 Programming and Data Analysis with R

## Assignment 2 (10 Marks) - Makeup

## Time-bound examination

## Due date: 14 September 2021, 8.00AM (Sri Lanka Standard Time)

We will NOT accept assignment submissions beyond this time.

Extensions of time for submission are only allowed for the categories mentioned here: 

https://hellor.netlify.app/2021/week0.html#10


# Assignment instructions

**Step 1**

Install `devtools` package.

**Step 2**

Type the following code to get access to the `sta3262` package. This package provides access to the assignment documents

```r
library(devtools)
devtools::install_github("thiyangt/sta3262")

```

**Step 3**

Load the `sta3262` using the command

```{r, comment=NA}
library(sta3262)
```

**Step 4**

Use the `get_assignment_data` function to get access to your assignment dataset. The function input is your index number.

Example:

```{r, comment=NA, eval=FALSE}
get_assignment_data("AS2018000") # this displays the dataset

```



**Step 5** 

Use the `get_assignment_questions` function to get access to your assignment questions. The function input is your index number without "AS". 

Write R codes to obtain answers to the questions. Use tidyverse packages and %>% operator in your coding. Do not use base R functions for plotting.



Example:

```{r, comment=NA}
get_assignment_questions(2018000) 

```

**Step 6**

Submit the following documents

1. R script file containing the R codes.
    
2. Upload both R codes and outputs in a PDF file. Please include your index number and e-signature.
